Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-07-17 manuscript_pretty.tex
working - incomplete

Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).

@@

One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information (Abrahamse, Braem, Notebaert, \& Verguts, 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities. As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion. However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.

@@

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\). Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

@@

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al\ldots{}. found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abrahamse_grounding_2016}{}%
Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016). Grounding cognitive control in associative learning. \emph{Psychological Bulletin}, \emph{142}, 693--728. doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}

\leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory statistical learning: Predictive frequency information affects the deployment of contextually mediated attentional resources on perceptual tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987. doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

\leavevmode\hypertarget{ref-blais_trial-by-trial_2015}{}%
Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015). Trial-by-trial adjustments in control triggered by incidentally encoded semantic cues. \emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930. doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}

\leavevmode\hypertarget{ref-brady_visual_2013}{}%
Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013). Visual long-term memory has the same limit on fidelity as visual working memory. \emph{Psychological Science}, \emph{24}, 981--990. doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}

@@

\leavevmode\hypertarget{ref-brosowsky_context-specific_2016}{}%
Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional sampling: Intentional control as a pre-requisite for contextual control. \emph{Consciousness and Cognition}, \emph{44}, 146--160. doi:\href{https://doi.org/10.1016/j.concog.2016.07.001}{10.1016/j.concog.2016.07.001}

\leavevmode\hypertarget{ref-brosowsky_memory-guided_2018}{}%
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective attention: Single experiences with conflict have long-lasting effects on cognitive control. \emph{Journal of Experimental Psychology: General}, \emph{147}, 1134--1153. doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

@@

\leavevmode\hypertarget{ref-bugg_support_2012}{}%
Bugg, J., \& Crump, M. J. (2012). In support of a distinction between voluntary and stimulus-driven control: A review of the literature on proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3}, 367. doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}

@@

\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of control in the Stroop task. \emph{Memory \& Cognition}, \emph{36}, 1484--1494. doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}

\leavevmode\hypertarget{ref-canadas_social_2013}{}%
Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013). Social categories as a context for the allocation of attentional control. \emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}

\leavevmode\hypertarget{ref-corballis_independent_2003}{}%
Corballis, P. M., \& Gratton, G. (2003). Independent control of processing strategies for different locations in the visual field. \emph{Biological Psychology}, \emph{64}, 191--209. doi:\href{https://doi.org/10.1016/S0301-0511(03)00109-1}{10.1016/S0301-0511(03)00109-1}

@@

\leavevmode\hypertarget{ref-crump_learning_2016}{}%
Crump, M. J. (2016). Learning to selectively attend from context-specific attentional histories: A demonstration and some constraints. \emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77. doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}

\leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the location-based context-specific proportion congruent effect for frequency unbiased items: A reply to Hutcheon and Spieler (2016). \emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807. doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}

\leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
Crump, M. J. C., \& Milliken, B. (2009). The flexibility of context-specific control: Evidence for context-driven generalization of item-specific control settings. \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532. doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}

@@

\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific proportion congruent Stroop effect: Location as a contextual cue. \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321. doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}

\leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific learning and control: The roles of awareness, task relevance, and relative salience. \emph{Consciousness and Cognition}, \emph{17}, 22--36. doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}

@@

\leavevmode\hypertarget{ref-egner_creatures_2014}{}%
Egner, T. (2014). Creatures of habit (and control): A multi-level learning perspective on the modulation of congruency effects. \emph{Frontiers in Psychology}, \emph{5}, 1247. doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}

\leavevmode\hypertarget{ref-eriksen_effects_1974}{}%
Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon the identification of a target letter in a nonsearch task. \emph{Perception \& Psychophysics}, \emph{16}, 143--149. doi:\href{https://doi.org/10.3758/BF03203267}{10.3758/BF03203267}

@@

\leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the generalizability of context-driven control. \emph{Quarterly Journal of Experimental Psychology}, \emph{70}, 1292--1304. doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}

\leavevmode\hypertarget{ref-hubner_location-specific_2016}{}%
Hübner, R., \& Mishra, S. (2016). Location-specific attentional control is also possible in the Simon task. \emph{Psychonomic Bulletin \& Review}, \emph{23}, 1867--1872. doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}

\leavevmode\hypertarget{ref-king_priming_2012}{}%
King, J. A., Korb, F. M., \& Egner, T. (2012). Priming of control: Implicit contextual cuing of top-down attentional set. \emph{The Journal of Neuroscience}, \emph{32}, 8192--8200. doi:\href{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}{10.1523/JNEUROSCI.0934-12.2012}

@@

\leavevmode\hypertarget{ref-logan_when_1979}{}%
Logan, G. D., \& Zbrodoff, N. J. (1979). When it helps to be misled: Facilitative effects of increasing the frequency of conflicting stimuli in a Stroop-like task. \emph{Memory \& Cognition}, \emph{7}, 166--174. doi:\href{https://doi.org/10.3758/BF03197535}{10.3758/BF03197535}

@@

\leavevmode\hypertarget{ref-ma_chicago_2015}{}%
Ma, D. S., Correll, J., \& Wittenbrink, B. (2015). The Chicago face database: A free stimulus set of faces and norming data. \emph{Behavior Research Methods}, \emph{47}, 1122--1135. doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}

@@

\leavevmode\hypertarget{ref-mayr_outsourcing_2007}{}%
Mayr, U., \& Bryck, R. L. (2007). Outsourcing control to the environment: Effects of stimulus/response locations on task selection. \emph{Psychological Research}, \emph{71}, 107--116. doi:\href{https://doi.org/10.1007/s00426-005-0039-x}{10.1007/s00426-005-0039-x}

\leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
Schmidt, J. R., \& Besner, D. (2008). The Stroop effect: Why proportion congruent has nothing to do with congruency and everything to do with contingency. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{34}, 514--523. doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}

\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}

\leavevmode\hypertarget{ref-tottenham_nimstim_2009}{}%
Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare, T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial expressions: Judgments from untrained research participants. \emph{Psychiatry Research}, \emph{168}, 242--249. doi:\href{https://doi.org/10.1016/j.psychres.2008.05.006}{10.1016/j.psychres.2008.05.006}

\leavevmode\hypertarget{ref-van_selst_solution_1994}{}%
Van Selst, M., \& Jolicoeur, P. (1994). A solution to the effect of sample size on outlier elimination. \emph{The Quarterly Journal of Experimental Psychology Section A}, \emph{47}, 631--650. doi:\href{https://doi.org/10.1080/14640749408401131}{10.1080/14640749408401131}

\leavevmode\hypertarget{ref-vietze_context_2009}{}%
Vietze, I., \& Wendt, M. (2009). Context specificity of conflict frequency-dependent control. \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400. doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}

\leavevmode\hypertarget{ref-weidler_transfer_2016}{}%
Weidler, B. J., \& Bugg, J. (2016). Transfer of location-specific control to untrained locations. \emph{The Quarterly Journal of Experimental Psychology}, \emph{69}, 2202--2217. doi:\href{https://doi.org/10.1080/17470218.2015.1111396}{10.1080/17470218.2015.1111396}

>>>>

Selective attention is commonly investigated using interference paradigms like the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).

@@

One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information (Abrahamse, Braem, Notebaert, \& Verguts, 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities. As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion. How associations between attentional priorities and context cues are formed and used still remains unclear however. The current study addresses two related issues.

First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how

Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the learning process to the automaticity of skill-learning ().

However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.

@@

\hypertarget{data-analysis}{%
\section{Data Analysis}\label{data-analysis}}

All analyses in this and the following experiments were performed in R (R Core Team, 2019) using a variety of R packages (). In particular, we used the afex and car packages (Fox \& Weisberg, 2019; Singmann, Bolker, Westfall, \& Aust, 2019) to perform all the Null Hypothesis Significance Tests, the BayesFactor package to perform Bayesian analyses (Morey \& Rouder, 2018), and the conflictPower package to perform the simulation-based sensitivity and power analyses (Crump \& Brosowsky, 2019). All data and scripts can be found

We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman.. 2009). Using conventional frequentist testing it is not possible to quantify the evidence for a null effect. Bayes Factors, however, quantify the degree to which the observed data are compatible with either the alternative or null hypothesis (Dienes, 2014; Rouder et al., 2014). All Bayesian analyses were performed using the R package BayesFactor Version XXXXX and Bayes Factors (BFs) were calculated using its default settings (Morey and Rouder, 2014). Following the guidelines recommended by Rouder et al.~(2009)

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 3,217.08\), \(p = .005\), \(\hat{\eta}^2_p = .061\) 90\% CI \([0.01\), \(0.14]\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) < 0.01\), \(\mathit{MSE} = 3,217.08\), \(p = .996\), \(\hat{\eta}^2_p < .001\) 90\% CI \([0\), \(1]\), showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 27.87\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 27.87\), \(p = .400\), \(\hat{\eta}^2_p = .014\). Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

@@

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al\ldots{}. found that\ldots{} In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

@@

\hypertarget{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}{%
\section{Estimating reproducability by simulation-based sensitivity- and power-analyses}\label{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}}

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure5-1.pdf}
\caption{\label{fig:figure5}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent). Task-relevance was manipulated through explicit instructions.}
\end{figure}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abrahamse_grounding_2016}{}%
Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016). Grounding cognitive control in associative learning. \emph{Psychological Bulletin}, \emph{142}, 693--728. \url{https://doi.org/10.1037/bul0000047}

\leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory statistical learning: Predictive frequency information affects the deployment of contextually mediated attentional resources on perceptual tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987. \url{https://doi.org/10.1080/20445911.2017.1353518}

\leavevmode\hypertarget{ref-blais_trial-by-trial_2015}{}%
Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015). Trial-by-trial adjustments in control triggered by incidentally encoded semantic cues. \emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930. \url{https://doi.org/10.1080/17470218.2014.1000346}

\leavevmode\hypertarget{ref-brady_visual_2013}{}%
Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013). Visual long-term memory has the same limit on fidelity as visual working memory. \emph{Psychological Science}, \emph{24}, 981--990. \url{https://doi.org/10.1177/0956797612465439}

@@

\leavevmode\hypertarget{ref-brosowsky_context-specific_2016}{}%
Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional sampling: Intentional control as a pre-requisite for contextual control. \emph{Consciousness and Cognition}, \emph{44}, 146--160. \url{https://doi.org/10.1016/j.concog.2016.07.001}

\leavevmode\hypertarget{ref-brosowsky_memory-guided_2018}{}%
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective attention: Single experiences with conflict have long-lasting effects on cognitive control. \emph{Journal of Experimental Psychology: General}, \emph{147}, 1134--1153. \url{https://doi.org/10.1037/xge0000431}

@@

\leavevmode\hypertarget{ref-bugg_support_2012}{}%
Bugg, J., \& Crump, M. J. (2012). In support of a distinction between voluntary and stimulus-driven control: A review of the literature on proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3}, 367. \url{https://doi.org/10.3389/fpsyg.2012.00367}

@@

\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of control in the Stroop task. \emph{Memory \& Cognition}, \emph{36}, 1484--1494. \url{https://doi.org/10.3758/MC.36.8.1484}

\leavevmode\hypertarget{ref-canadas_social_2013}{}%
Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013). Social categories as a context for the allocation of attentional control. \emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943. \url{https://doi.org/10.1037/a0029794}

\leavevmode\hypertarget{ref-corballis_independent_2003}{}%
Corballis, P. M., \& Gratton, G. (2003). Independent control of processing strategies for different locations in the visual field. \emph{Biological Psychology}, \emph{64}, 191--209. \url{https://doi.org/10.1016/S0301-0511(03)00109-1}

@@

\leavevmode\hypertarget{ref-crump_learning_2016}{}%
Crump, M. J. (2016). Learning to selectively attend from context-specific attentional histories: A demonstration and some constraints. \emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77. \url{https://doi.org/10.1037/cep0000066}

\leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the location-based context-specific proportion congruent effect for frequency unbiased items: A reply to Hutcheon and Spieler (2016). \emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807. \url{https://doi.org/10.1080/17470218.2016.1206130}

\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}.

\leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
Crump, M. J. C., \& Milliken, B. (2009). The flexibility of context-specific control: Evidence for context-driven generalization of item-specific control settings. \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532. \url{https://doi.org/10.1080/17470210902752096}

@@

\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific proportion congruent Stroop effect: Location as a contextual cue. \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321. \url{https://doi.org/10.3758/BF03193850}

\leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific learning and control: The roles of awareness, task relevance, and relative salience. \emph{Consciousness and Cognition}, \emph{17}, 22--36. \url{https://doi.org/10.1016/j.concog.2007.01.004}

@@

\leavevmode\hypertarget{ref-egner_creatures_2014}{}%
Egner, T. (2014). Creatures of habit (and control): A multi-level learning perspective on the modulation of congruency effects. \emph{Frontiers in Psychology}, \emph{5}, 1247. \url{https://doi.org/10.3389/fpsyg.2014.01247}

\leavevmode\hypertarget{ref-eriksen_effects_1974}{}%
Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon the identification of a target letter in a nonsearch task. \emph{Perception \& Psychophysics}, \emph{16}, 143--149. \url{https://doi.org/10.3758/BF03203267}

@@

\leavevmode\hypertarget{ref-r_car_2019}{}%
Fox, J., \& Weisberg, S. (2019). \emph{An R companion to applied regression} (Third). Thousand Oaks CA: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}

\leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the generalizability of context-driven control. \emph{Quarterly Journal of Experimental Psychology}, \emph{70}, 1292--1304. \url{https://doi.org/10.1080/17470218.2016.1182193}

\leavevmode\hypertarget{ref-hubner_location-specific_2016}{}%
Hübner, R., \& Mishra, S. (2016). Location-specific attentional control is also possible in the Simon task. \emph{Psychonomic Bulletin \& Review}, \emph{23}, 1867--1872. \url{https://doi.org/10.3758/s13423-016-1057-y}

\leavevmode\hypertarget{ref-king_priming_2012}{}%
King, J. A., Korb, F. M., \& Egner, T. (2012). Priming of control: Implicit contextual cuing of top-down attentional set. \emph{The Journal of Neuroscience}, \emph{32}, 8192--8200. \url{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}

@@

\leavevmode\hypertarget{ref-logan_when_1979}{}%
Logan, G. D., \& Zbrodoff, N. J. (1979). When it helps to be misled: Facilitative effects of increasing the frequency of conflicting stimuli in a Stroop-like task. \emph{Memory \& Cognition}, \emph{7}, 166--174. \url{https://doi.org/10.3758/BF03197535}

@@

\leavevmode\hypertarget{ref-ma_chicago_2015}{}%
Ma, D. S., Correll, J., \& Wittenbrink, B. (2015). The Chicago face database: A free stimulus set of faces and norming data. \emph{Behavior Research Methods}, \emph{47}, 1122--1135. \url{https://doi.org/10.3758/s13428-014-0532-5}

@@

\leavevmode\hypertarget{ref-mayr_outsourcing_2007}{}%
Mayr, U., \& Bryck, R. L. (2007). Outsourcing control to the environment: Effects of stimulus/response locations on task selection. \emph{Psychological Research}, \emph{71}, 107--116. \url{https://doi.org/10.1007/s00426-005-0039-x}

\leavevmode\hypertarget{ref-r_bayesfactor_2018}{}%
Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. Retrieved from \url{https://CRAN.R-project.org/package=BayesFactor}

\leavevmode\hypertarget{ref-r_software_2019}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
Schmidt, J. R., \& Besner, D. (2008). The Stroop effect: Why proportion congruent has nothing to do with congruency and everything to do with contingency. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{34}, 514--523. \url{https://doi.org/10.1037/0278-7393.34.3.514}

\leavevmode\hypertarget{ref-r_afex_2019}{}%
Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2019). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}

\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. \url{https://doi.org/10.1037/h0054651}

\leavevmode\hypertarget{ref-tottenham_nimstim_2009}{}%
Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare, T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial expressions: Judgments from untrained research participants. \emph{Psychiatry Research}, \emph{168}, 242--249. \url{https://doi.org/10.1016/j.psychres.2008.05.006}

\leavevmode\hypertarget{ref-van_selst_solution_1994}{}%
Van Selst, M., \& Jolicoeur, P. (1994). A solution to the effect of sample size on outlier elimination. \emph{The Quarterly Journal of Experimental Psychology Section A}, \emph{47}, 631--650. \url{https://doi.org/10.1080/14640749408401131}

\leavevmode\hypertarget{ref-vietze_context_2009}{}%
Vietze, I., \& Wendt, M. (2009). Context specificity of conflict frequency-dependent control. \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400. \url{https://doi.org/10.1080/17470210802426908}

\leavevmode\hypertarget{ref-weidler_transfer_2016}{}%
Weidler, B. J., \& Bugg, J. (2016). Transfer of location-specific control to untrained locations. \emph{The Quarterly Journal of Experimental Psychology}, \emph{69}, 2202--2217. \url{https://doi.org/10.1080/17470218.2015.1111396}
